---
output: 
  html_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>', fig.path = "README-")
```

## Overview
 
"roller" is a R package that utilizes several functions in order to 
simulate rolling an object with distinct sides.
- device() creates an object belonging to the "device" class that has 
sides and probabilties associated with those sides
- roll() creates an object belonging to the "rolls" class that rolls a 
"device" a certain number of times according to its sides and 
probabilities
- is.device() tests whether an object belongs to the "device" class
- print.device() prints a "device" object as a data frame with a header
- summary.rolls() returns a summary of a "rolls" object that includes 
the sides of its "device" parameter, the number of times each side was 
rolled, and the proportions of the rolls on which each side was rolled.
- plot.rolls() takes a "rolls" object and displays a barplot of the 
frequencies of the "device" parameter's sides in the rolls.
- The extraction method "[" returns the "device" side rolled on a 
specific roll corresponding to an index.
- The replacement method "[<-" replaces the "device" side rolled on 
a specific roll corresponding to an index with another "device" side
- The addition method "+" adds new rolls to a "rolls" object

## Installation

Use one of these functions to install "roller" version from GitHub 
(with or without vignette). Install "devtools" package if needed.

```{r}
#install.packages("devtools")
#devtools::install_github("harinandansrikanth/stat133-hws-fall18/roller")
#devtools::install_github("harinandansrikanth/stat133-hws-fall18/roller", build_vignettes = TRUE)
```
## Usage

```{r}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(devtools)
library(dplyr)
library(roller)

#default device object
dev1 <- device()
dev1

#non-default object
dev2 <- device(sides = c('q','w','e'), prob = c((1/4),(1/2),(1/4)))
dev2

#rolls object
rolls1 <- roll(dev1,5)
rolls1

#rolls object
rolls2 <- roll(dev2,12)
rolls2

#is.device()
is.device(device(c("a","b"),c(0.4,0.6)))
is.device(c(0.5,0.5))

#device()
device_example <- device(sides = c("g","h","j"), prob = c(0.3,0.5,0.2))
device_example
print(device_example)

#roll() (class of object is `rolls`, not roll)
set.seed(123)
rolls_example <- roll(device(sides = c(1,2,3,4), prob = c(0.1, 0.2, 0.4, 0.3)), times = 25)
rolls_example

#summary of rolls object
summary(rolls_example)

#plot
plot(rolls_example)

#extraction
rolls_example[14]

#replacement
rolls_example[14] <- 2

#rolls_example #The new rolls_example after replacement
rolls_example[14]

#addition
rolls_example + 15
```
