---
title: "Workout 1 Markdown"
author: "Harinandan Srikanth"
date: "September 30, 2018"
output: github_document
---

```{r setup, include=FALSE}
setwd('C:/Users/Harinandan/OneDrive/Documents/Fall 2018/Stat 133/Homework/Workout 1/report')
knitr::opts_chunk$set(echo = TRUE, fig.path = 'workout01-harinandan-srikanth_files/')
```



```{r }
library(ggplot2)
library(readr)
library(dplyr)

dat_nba <- read_csv('../data/nba2018-teams.csv')

dat_nba_sbyt <- summarise(group_by(dat_nba, team), total_salary = sum(salary))
dat_nba_sbyt <- arrange(dat_nba_sbyt, total_salary)
dat_nba_sbyt$team <- factor(dat_nba_sbyt$team, levels = dat_nba_sbyt$team, ordered = TRUE)
```

```{r scatterplot1}
bar_team_salary <- ggplot(data=dat_nba_sbyt, aes(x=dat_nba_sbyt$team, y=dat_nba_sbyt$total_salary)) + geom_col() + xlab("Team") + ylab("Salary (in millions)") + geom_hline(aes(yintercept=mean(dat_nba_sbyt$total_salary)), color='red', size = 3, alpha=0.6) + coord_flip()
bar_team_salary
```


```{r }
dat_nba_points <- summarise(group_by(dat_nba, team), total_points = sum(points))
dat_nba_points <- arrange(dat_nba_points, total_points)
dat_nba_points$team <- factor(dat_nba_points$team, levels = dat_nba_points$team, ordered = TRUE)
dat_nba_points
```


```{r scatterplot2}
bar_team_points <- ggplot(data=dat_nba_points, aes(x=dat_nba_points$team,y=dat_nba_points$total_points)) + geom_col() + xlab("Team") + ylab("Points") + geom_hline(aes(yintercept=mean(dat_nba_points$total_points)), color='green', size=3, alpha=0.6) + coord_flip()
bar_team_points
```


```{r}
dat_nba_eff <- summarise(group_by(dat_nba, team), total_efficiency = sum(efficiency))
dat_nba_eff <- arrange(dat_nba_eff, total_efficiency)
dat_nba_eff$team <- factor(dat_nba_eff$team, levels = dat_nba_eff$team, ordered = TRUE)
dat_nba_eff
```


```{r scatterplot3}
bar_team_eff <- ggplot(data=dat_nba_eff, aes(x=dat_nba_eff$team,y=dat_nba_eff$total_efficiency)) + geom_col() + xlab("Team") + ylab("Efficiency") + geom_hline(aes(yintercept=mean(dat_nba_eff$total_efficiency)), color='yellow', size=3, alpha=0.6) + coord_flip()
bar_team_eff
```


```{r }
# ignoring missed free throws and missed field goals for the dollar efficiency calculation
dollar_eff <- (dat_nba$points + dat_nba$off_rebounds + dat_nba$def_rebounds + dat_nba$assists + dat_nba$steals + dat_nba$blocks - dat_nba$turnovers) / dat_nba$salary 
dat_nba <- mutate(dat_nba, dollar_efficiency=dollar_eff) 

dat_nba_dollar_eff <- summarise(group_by(dat_nba, team), total_dollar_eff = sum(dollar_efficiency))
dat_nba_dollar_eff <- arrange(dat_nba_dollar_eff, total_dollar_eff)
dat_nba_dollar_eff$team <- factor(dat_nba_dollar_eff$team, levels = dat_nba_dollar_eff$team, ordered = TRUE)
dat_nba_dollar_eff

```


```{r scatterplot4}
bar_team_dollar_eff <- ggplot(data=dat_nba_dollar_eff, aes(x=dat_nba_dollar_eff$team,y=dat_nba_dollar_eff$total_dollar_eff)) + geom_col() + xlab("Team") + ylab("Efficiency") + geom_hline(aes(yintercept=mean(dat_nba_dollar_eff$total_dollar_eff)), color='blue', size=3, alpha=0.6) + coord_flip()
bar_team_dollar_eff

```

Rational behind dollar_efficiency: This index measures how many points each team is winning for the amount money that the investor(s) of that team is paying it. This is a good index for ranking teams because a team will be ranked higher if the amount of money an investor is spending on it is worth it.

```{r pressure, echo=FALSE}

```

* Was this your first time working on a project with such file structure? If yes, how do you feel about it?
  + Yes. I find it very interesting that the sink function allows you to both create a file and add content to that file while only operating in R and not even opening the file.
* Was this your first time using relative paths? If yes, can you tell why they are important for reproducibility purposes?
  + No. I have used relative paths in Git Bash in previous assignments for this class.
* Was this your first time using an R script? If yes, what do you think about just writing code (without markdown syntax)?
  + No.
* What things were hard, even though you saw them in class/lab?
 + I personally feel that for this assignment, there was nothing that we saw in class or lab that ended up being hard for me in this assignment. 
* What was easy(-ish) even though we haven't done it in class/lab?
  + Even though we hadn't done it in class, creating the bar charts was easy once I figured out which graphical functions to use.
* Did anyone help you completing the assignment? If so, who?
  + No one helped me in completing this assignment. The only help I got was from the internet when I was researching how to turn the bar charts sideways.
* How much time did it take to complete this HW?
  + It took about 8 hours to complete this homework.
* What was the most time consuming part?
  + The most time consuming part was creating the dictionary and describing every column label.
* Was there anything interesting?
  + I think the sink function was really interesting because of how convenient it was for creating files and adding content to them.
